% ============================================================================
% PAPER 2 SUPPLEMENT (method line, M1). Created in the editorial restructure
% that compressed the main text to one storyline; every technical block here
% was MOVED from main_m1.tex (or from the frozen rulings) verbatim, not
% reworded. Sections:
%   S1 framework theorem (R14 Candidate A, full generalized-KKT system)
%   S2 alignment proposition (R14 Candidate C, full statement + failure modes)
%   S3 design machinery in full (certificate math, guards, dictionary,
%      subspace conventions, budget accounting)  [R10/R11/R13]
%   S4 Monte-Carlo verification detail (grid + zoom + replication runs)
%   S5 secondary-arm full results (M1 \SPH placeholders)
%   S6 proofs (R14-SUPP \SPH)
% PLACEHOLDER DISCIPLINE: \SPH sites here are indexed in the same
% PLACEHOLDER_LEDGER.md as the main text.
% ============================================================================
\documentclass[10pt]{article}
\usepackage{amsmath,amssymb,bm}
\usepackage{graphicx}
\usepackage[margin=2.5cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\newcommand{\SPH}[1]{\textcolor{red}{[#1]}}   % unfilled campaign placeholder
\newcommand{\rhobar}{\bar{\rho}}
\newcommand{\Cu}{C_{u}}
\newcommand{\rhoR}{\rho_{R}}
\newcommand{\Jex}{J_{\mathrm{exact}}}
\newtheorem{proposition}{Proposition}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\theproposition}{S\arabic{proposition}}

\title{Supplement:\ Information-optimal illumination for dead-time-limited
single-pixel imaging}
\author{\SPH{author block --- user decision (mirrors main text)}}
\date{}

\begin{document}
\maketitle

Numbering ``Theorem 1--3'' below refers to the main text; equations and
propositions local to this supplement carry the S-prefix. All frozen
constants trace to the R10/R11/R13/R14 rulings cited in the main-text source
comments.

% ===========================================================================
\section{The framework theorem: one master concave program}
\label{sec:s-framework}
% MOVED verbatim from the pre-restructure main text (R14 Candidate A,
% approved as the framework theorem; frozen discrete-optima caveat verbatim).
The framework theorem generalizes the main-text design program:\ with the
random-hold kernel $J_H(\rho,\nu)$ of Theorem~2 inside the
rank-one atoms $H_z = \nu J_H(\rho_z,\nu)\,q_z q_z^{\top}$, the
design-measure problem remains concave, and every
true interior optimum of the declared problem satisfies one generalized
reduced-sensitivity/KKT system:\ the sensitivity
$\psi(z) = M\,\mathrm{tr}[V^{-1}H_z] - \sum_m \beta_m c_m(z)$ obeys
$\psi(z)\le\eta$ with equality on support atoms, and at any support atom
interior in a smooth scalar coordinate $y$, $\partial_y\psi = 0$ with
$\partial^2_y\psi \le 0$. The load coordinate yields the
information-water-filling equation --- $M\nu J_H'(\rho)\,\ell$ equal to the
marginal resource shadow price, with $\ell = q^{\top}V^{-1}q$ --- while the
support-scale and weight-power coordinates equate
$2M\nu J_H(\rho)\,q_y^{\top}V^{-1}q$ to the corresponding marginal
dose/peak/dispersion price:\ the apparent ``conditioning penalty'' is not an
ad hoc term but the $V^{-1}$ geometry inside the reduced sensitivity, which
also explains why raising proxy contrast from $p=1$ to $p=2$ can lower the
true objective. One caveat is kept deliberately:\ the master design problem
places load, support scale, and intensity weighting in one constrained
concave measure optimization, and its support atoms satisfy a common
reduced-sensitivity condition; but the empirically observed occupancy
($k\approx32$) and weighting ($p\approx1$) optima \emph{motivate} these
coordinates and are not themselves claimed as continuous KKT theorems ---
they were selected from discrete grids and judged by image endpoints, not by
the master $\log\det$ objective.

% ===========================================================================
\section{The alignment proposition}
\label{sec:s-alignment}
% MOVED verbatim from the pre-restructure main text (R14 Candidate C,
% approved as a conditional proposition, NOT a universal approximation
% theorem; frozen wording preserved).
At a fixed design iterate with directional values
$\ell_i = q_i^{\top}V^{-1}q_i$, allocate scalar loads under the budget
$\sum_i \pi_i\rho_i = B$ to maximize $F(\rho) = \sum_i \pi_i\ell_i
J(\rho_i)$; on an interval where $J$ is increasing and strictly concave, the
water-filling optimum satisfies $\ell_i J'(\rho_i^{*}) = \beta$ at every
interior coordinate. A single global source induces
$\tilde\rho_i = \kappa u_i$, with $u_i = a_i^{\top}x$ the bucket brightness.

\begin{proposition}[alignment and residual bound]
\label{prop:s-alignment}
The fixed-flux allocation is exactly optimal for this scalar subproblem if
and only if there exists $\beta$ with
\begin{equation}
  \ell_i\,J'(\kappa u_i) = \beta
  \label{eq:s-alignment}
\end{equation}
for all interior active directions, with KKT-compatible inequalities at the
bounds. If moreover $-\ell_i J''(\rho) \ge m > 0$ throughout the admitted
interval, then, with residuals $r_i = \ell_i J'(\kappa u_i) - \beta$,
\begin{equation}
  0 \;\le\; F(\rho^{*}) - F(\tilde\rho)
  \;\le\; \frac{1}{2m}\sum_i \pi_i\, r_i^{2}.
  \label{eq:s-residual}
\end{equation}
\end{proposition}

A computable projected-KKT residual --- not $\Cu$ alone --- therefore
certifies whether one global flux knob is close to the scalar water-filling
optimum. In power-law form, if $J'(\rho)\asymp C\rho^{-s}$ and
$\ell_i \asymp u_i^{\alpha}$, fixed flux aligns when $\alpha\approx s$; for
the rising kernel $J = \rho/(1+\rho)$ the local slope
$s(\rho) = 2\rho/(1+\rho)$ runs from $0$ toward $2$, so the often-invoked
$\ell \propto u^{2}$ alignment is only a high-load approximation. Without the
alignment condition there is no scene-independent constant-factor
guarantee:\ two directions with $u_1/u_2\to\infty$ but $\ell_1/\ell_2\to0$
drive the fixed-flux objective ratio to zero, so fixed flux can be
arbitrarily bad. With random holds, $J'$ vanishes at the jitter cap and is
negative beyond it, so fixed flux can overdrive the brightest directions and
explicit gain control becomes necessary. This explains both sides of the
companion's dev evidence~\cite{companion}:\ \textsc{RIDGE-FIXED} with one
global knob is near-optimal exactly when its realized residuals are small
(self-water-filling), while the uniform servo --- which loses by up to
$\sim7$~dB on sparse-support scenes --- fails because forcing equal $\rho_i$
discards a naturally favorable alignment between $u_i$ and $\ell_i$.

% ===========================================================================
\section{Design machinery in full}
\label{sec:s-machinery}

\subsection{Task subspace and numerical ridge}
% From R13 §6 (moved from the pre-restructure main §2.1 tail).
The estimable subspace is frozen at $r = 200$:\ $B$ is
the top-$200$ eigenbasis of the fixed comparator's information matrix under
the same pre-scan, dwell, and resource convention, computed before the
optimization and held fixed, with a fixed numerical ridge
$\epsilon_0 = 10^{-9}\,\mathrm{tr}(B^{\top}V_{\text{FIXED}^\ast}B)/r$
(R13~\S6). A design-dependent ridge is not permitted:\ it would change the
objective derivative and invalidate the sensitivity calculation.

\subsection{The equivalence certificate}
% MOVED verbatim from the pre-restructure main §2.2.
By concavity of $\log\det$ and affineness of $\xi\mapsto V(\xi)$, a feasible
design $\xi^\ast$ is optimal iff there exist constraint multipliers such that
the reduced sensitivity
$s(a) = \mathrm{tr}[V(\xi^\ast)^{-1}H(a)] - \sum_j\alpha_j e_j(a)
- \sum_k\beta_k c_k(a)$ satisfies $s(a) \le \eta^\ast$ over $\mathcal{A}$ with
equality on the support (the constrained Kiefer--Wolfowitz / general
equivalence theorem for nonlinear
models~\cite{kiefer1959optimum,white1973equivalence}). Because a strict
per-pixel-dose dual is not yet implemented, the frozen confirmatory quantity
is the conservative additive budget-dual bound: with
$d_a = \mathrm{tr}(V^{-1} M_{\mathrm{main}} H_a)$, $c_a = \rho_a$, budget
$c^{\top}\xi \le b$, and $\theta \ge 0$,
\begin{equation}
  \begin{aligned}
  G_{\mathrm{rel}} &= \max_a(d_a - \theta c_a) - \sum_a \xi_a(d_a - \theta c_a)
  + \theta\{b - c^{\top}\xi\},\\
  &\qquad\qquad G_{\mathrm{rel}}/r \le 10^{-3},
  \end{aligned}
  \label{eq:s-relkw}
\end{equation}
which upper-bounds the gap to the optimum of the relaxed (dose-free)
problem and hence to the dose-constrained optimum (R13~\S6.1). It is reported
as \texttt{RELAXED\_KW\_UPPER\_BOUND}, relative to the frozen dictionary and
local estimate, not as a full per-pixel equivalence certificate. The maximum
is taken by an exact scan of the frozen dictionary; a learned proposer may
warm-start the search but the frozen run finishes with the exact
oracle~\cite{jaggi2013frankwolfe}. Continuous weights are rounded to an exact
$972$-row design by efficient rounding followed by deterministic
exchange~\cite{pukelsheim1992rounding,nikolov2022volume,sagnol2015exact},
admissible only if the exact D-efficiency $\ge 0.95$.

\subsection{Guards as constraints}
% MOVED verbatim from the pre-restructure main §2.4.
The raw optimum is admissible only after all frozen guards pass; each is a
constraint of the master program or a post-rounding check, not a tunable
proxy. \emph{Peak (two-part, R13~A2):} a shape guard bounds unit-load support
weights to $\tfrac14 \le w_j \le 4$ with support size $k \ge 16$, and a
physical guard caps $\max_{i,j} a^{\mathrm{physical}}_{ij} \le 1536$ (the peak
of a uniform $k=16$ atom at the absolute load cap $\rho = 24$), so
matched-intensity ridge atoms cannot silently demand more peak power.
\emph{Weight power (R10~G4):} the dictionary contains powers $p\in\{0,1\}$
only; $p=2$ is excluded because dev evidence showed higher proxy contrast can
worsen conditioning and endpoint quality. \emph{Per-pixel dose (R10~G5):}
each pixel's mean exposure stays within $\pm5\%$ of the image mean, enforced
in-optimizer and re-verified after rounding; a necessary row bound follows,
$\rho_r \le 1.05\,M\bar d/\max_j g_{rj}$ (R13~A5). \emph{Spectral floor
(R10~G6):} $V_{\mathrm{OED}} \succeq 0.5\,V_{\text{FIXED}^\ast}$ on $B$, with a
convex-mixture fallback whose coefficient is fixed from information matrices
before any image endpoint is seen. \emph{Kernel and trust (R11~G7--G8,
R13~A1):} every $(\nu,\rho)$ node is certified for exact-PMF mass, score, and
derivative agreement, mean-information efficiency
$J_{\mathrm{mean}}/\Jex \ge 0.90$, finite-window RQL log-load bias
$|\log(\rho^{\dagger}/\rho)| \le 0.05$, ceiling probability
$p_{\mathrm{ceil}}(\rho,\nu)\le 0.05$ per atom and $\le 0.01$ design-weighted.
\emph{A-risk (R10~G7):} $\mathrm{tr}(V_{\mathrm{exact}}^{-1}) \le 1.05\,
\mathrm{tr}(V_{\text{FIXED}^\ast}^{-1})$. Any violation is a declared failure
state (\texttt{DICTIONARY\_RANK\_FAIL}, \texttt{CONTINUOUS\_CERTIFICATE\_FAIL},
\texttt{SPECTRAL\_GUARD\_FAIL}, \texttt{A\_RISK\_GUARD\_FAIL},
\texttt{DOSE\_GUARD\_FAIL}, \texttt{ROUNDING\_FAIL}), whose predeclared
fallback is the fixed comparator; no threshold is retuned after freeze.

\subsection{The frozen dictionary}
% R10 Q7 §5 minimum dictionary as amended by R13 §3.
The exact searchable dictionary includes all cyclic translates of:\
scattered balanced supports at $k=16$ and $k=32$; the solid $4\times4$
patch; the committed \textsc{Lblob}$6\times6$ 16-pixel support;
bars/rectangles $1\times16$, $2\times8$, $4\times4$, $8\times2$,
$16\times1$; compact 32-pixel square/rectangle variants; and the frozen
16-pixel ring/annulus family --- with $p=0$ and guarded $p=1$ weights for
every applicable support. The implementation supports variable $k$; all
translation families use the circulant/FFT evaluator, and the dictionary
manifest carries every family, translation, power, support size, and
SHA256.

\subsection{Budget accounting}
% R11 §4.3 dual reporting.
For every arm both the incident budget $B_{\mathrm{inc}} = \sum_i
\lambda_{s,i} T$ and the detected budgets $B_{\mathrm{det}}^{\mathrm{pred}}
= \sum_i \mathbb{E}[N_i]$, $B_{\mathrm{det}}^{\mathrm{obs}} = \sum_i N_i$
are reported, together with total and maximum per-pixel dose.
$B_{\mathrm{det}}$ may serve as an electronics-throughput guard if a
hardware limit is frozen before confirmation, but it is never the sole
fairness constraint:\ for a nonparalyzable detector
$\mathbb{E}[N\mid\rho]\simeq\nu\rho/(1+\rho)$, whose marginal cost tends to
zero at high load, so a detected-count-only budget can permit arbitrarily
large incident power while appearing nearly cost-free.

% ===========================================================================
\section{Monte-Carlo verification detail}
\label{sec:s-verification}
% MOVED verbatim from the pre-restructure main §5.7 (grid + zoom/replication
% paragraphs). Sources of record: results/round63_study2/
% jitter_sfi_v2_nu2000.log + _nu200.log; docs/R14_PREREGISTERED_PREDICTIONS.md
% (commits 8a627bb, 1d8d7aa, 5e51088, 1a32758, 4d8310d, bd731d5).
The refined sweep (\texttt{jitter\_sfi\_v2}:\ lognormal holds, $100{,}000$
frames per cell, common random numbers, 25-point log grid of spacing
$1.157$, $\nu \in \{200, 2000\}$) confirmed the R14 law out-of-sample. At
$\nu = 2000$ the measured peaks are $\rho_{*} = 22.297$, $10.739$, $5.173$,
$3.862$, $2.153$, and $1.607$ at $c_v = 0$, $0.02$, $0.05$, $0.1$, $0.2$,
and $0.3$, respectively; both predictions
registered before the data existed hit --- $c_v = 0.02$ predicted
$\approx10.4$, measured $10.739$ ($3\%$); $c_v = 0.2$ predicted
$\approx2.30$, measured $2.153$ ($6\%$) --- and every in-sample peak lies
within one grid notch of its exact-law value (commits \texttt{8a627bb},
predictions registered pre-data; \texttt{1d8d7aa}, verdict). The $\nu = 200$
column is consistent with the crossover correction:\ the $c_v = 0$ peak at
$9.28$ tracks the exact ridge $10.04$, and $c_v = 0.3$ measures $1.86$
against the predicted $1.77$.

A continuous-peak zoom (quadratic interpolation, local run, $150{,}000$
frames) and an independent replication (Colab, $400{,}000$ frames) then
measured the four jittered peaks twice each at $\nu = 2000$:\ local
$9.645$, $5.154$, $3.752$, $2.106$ and replicated $9.610$, $5.700$,
$3.399$, $2.051$ at $c_v = 0.02$, $0.05$, $0.1$, $0.2$, respectively. The pooled eight-measurement log-log fit gives slope $-0.658$
vs.\ the predicted $-2/3$ ($1.3\%$); the constant sits about $5\%$ below
$2^{-1/3}$, at the edge of the run-to-run noise, so the frozen statement
is:\ exponent confirmed at $1.3\%$, constant consistent within $5$--$10\%$.
The end points replicate a mild $\approx{-8}\%$ low bias across both runs,
left as an open higher-order note (candidate:\ a lognormal third-moment
correction to the leading finite-variance law). One intermediate hypothesis
is on the record:\ after the first two zoom points, an effective jitter-cost
multiplier $k = 4/3$ was preregistered (commit \texttt{5e51088}) and was
refuted by the very next measured point, whose deviation flipped sign
(commit \texttt{1a32758}) --- peak-location noise on flat information tops,
not a systematic constant. The fuller three-hold-family exponent battery
frozen in the ruling (tests E1--E5, with matched-CV gamma and bounded
two-point holds and cross-fitted conditional-score estimation) remains a
preregistered extension beyond this verdict.

% ===========================================================================
\section{Secondary-arm full results}
\label{sec:s-secondary}
\subsection{RIDGE-FIXED operating-point demonstration}
\SPH{M1: fixed-dwell gain per dwell of the ridge-tracking policy over
$\rhobar=0.60$ and safe references, realized loads, requested vs.\ achieved
mean load, RIDGE\_GUARD\_CLIPPED flags, and ceiling fractions.}

\subsection{OED-EQLOAD kernel ablation}
\SPH{M1: equal-load geometry vs.\ variable-load geometry --- any design
difference attributable to the renewal kernel, with numerical-noise
disclosure.}

\subsection{Certificate and rounding diagnostics}
\SPH{M1: relaxed-KW gap $G_{\mathrm{rel}}/r$, exact D-efficiency, A-risk
ratio, and spectral-floor margin per designed cell.}

% ===========================================================================
\section{Proofs}
\label{sec:s-proofs}
\SPH{supplement proofs at manuscript rigor: Theorems 1--3 (missing-information
identity via the martingale/law-of-total-variance argument; long-window rate
via the renewal local normal approximation; cubic optimum and small-jitter
expansion) and Proposition~\ref{prop:s-alignment}; per the R14 ruling these
are provable immediately, while the uniform two-parameter crossover requires
a dedicated triangular-array renewal local-limit argument or retains its
prediction label.}

\bibliographystyle{unsrt}
\bibliography{refs}

\end{document}
