% =====================================================================
%  Supplemental Material for
%  "Strong Optical Disorder Erases Images but Preserves Local Change
%   Observability"  (Rank-Jet Separation)
%  S1-S5 per R43 section 6.5. Audit trail, not an alternate manuscript.
%  Every number traces to paper_prl/CLAIM_SOURCE_MATRIX.md.
% =====================================================================
\documentclass[aps,prl,onecolumn,notitlepage,nofootinbib,superscriptaddress]{revtex4-2}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{booktabs}
\graphicspath{{figures/}}

\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}

\newcommand{\Treq}{T_{\mathrm{req}}}
\newcommand{\Cstar}{C_{\ast}}
\newcommand{\tr}{\operatorname{tr}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\eps}{\varepsilon}

\begin{document}

\title{Supplemental Material:\\
Strong Optical Disorder Erases Images but Preserves Local Change Observability}
\author{[AUTHORS]}
\affiliation{[AFFILIATION]}
\date{\today}
\maketitle

\noindent
This Supplemental Material is an audit trail for the Letter. It contains
(S1) the general Chernoff/Kullback--Leibler jet derivation and its equality
cases; (S2) the JET\_TEST design with all seventeen frozen checks and the raw
exponent tables; (S3) the full-scramble Gaussian derivation, exact generator,
rank-one result, and detection duel; (S4) the sealed thin-screen protocol with
bars D0--D6, the fixed/fresh comparator, the D3/D5 boundary failures, and the
chunking audit; and (S5) the thin-screen covariance aperture and a minimal
prior-art fence. All numerical values are read from the committed frozen
artifacts \texttt{JET\_TEST} (\texttt{1bf29f1}), \texttt{SCRAMBLE\_EXT}
(\texttt{ed7a1e0}), and \texttt{SEALED\_DET/CONFIRMATORY} (\texttt{b37c841}); no
new data are generated here.

% =====================================================================
\section{General quotient-jet derivation and equality cases}
% =====================================================================
Let $P_{\eps,\eta}$ be a dominated statistical model in which $\eps$ is a scalar
physical-change amplitude along a scene direction $\delta$ and $\eta$ is a
nuisance. Define the profiled Chernoff distance
\begin{equation}
\Cstar(\eps)=\inf_{\eta'}\ \max_{0\le s\le1}
\Big[-\log\!\int p_{\eps,\eta}^{\,s}\,p_{0,\eta'}^{\,1-s}\Big],
\label{eq:s_cstar}
\end{equation}
and assume the infimum is attained locally with
\begin{equation}
\Cstar(\eps)=c_m\,\eps^{2m}+o(\eps^{2m}),\qquad c_m>0 .
\label{eq:s_contact}
\end{equation}

\paragraph*{Theorem A (information-jet detection law).}
For $T$ independent observations with equal priors,
\begin{equation}
\lim_{T\to\infty}-\tfrac{1}{T}\log P_e^{\ast}(T,\eps)=\Cstar(\eps),
\end{equation}
so in the joint small-change/large-sample regime with target error exponent $h$,
\begin{equation}
\Treq(\eps)=\frac{h}{c_m\,\eps^{2m}}\,[1+o(1)] .
\label{eq:s_Treq}
\end{equation}
For quickest detection at false-alarm level $\alpha$, if the profiled per-bank KL
distance is $D_{\ast}(\eps)=k_m\eps^{2m}+o(\eps^{2m})$, then Lorden/CUSUM
asymptotics give the mean delay $E_{\mathrm{delay}}=|\log\alpha|/(k_m\eps^{2m})
[1+o(1)]$. The exponent $m$ is invariant because reparameterizing $\eta$ leaves
the nuisance orbit unchanged, a gain gauge absorbed into $\eta$ is quotiented
automatically, no statistic or Fisher eigenbasis is selected, and physical
covariation changes $c_m$ but not the definition of $m$. The contact order $m$ is
robust to an unknown nuisance $\eta$: for a truly unknown $\eta$ the fixed-error
\emph{constant} is a composite-hypothesis quantity (a least-favorable-nuisance /
GLRT exponent) for which the profiled Chernoff distance is a bound, but the
exponent $m$ itself is unchanged.

\paragraph*{Gaussian specialization.}
Let $P_\eps=\mathcal{N}(0,\Sigma_\eps)$ with
$\Sigma_\eps=\Sigma_0+z(\eps)H$, $\Sigma_0\succ0$, and put
$A_\eps=z(\eps)K$, $K=\Sigma_0^{-1/2}H\Sigma_0^{-1/2}$. The exact divergences are
\begin{align}
D(P_\eps\|P_0)&=\tfrac12\big[\tr A_\eps-\log\det(I+A_\eps)\big]
   = \frac{z^2}{4}\tr(K^2)-\frac{z^3}{6}\tr(K^3)+O(z^4),
\label{eq:s_KL}\\
B(P_\eps,P_0)&=\tfrac12\log\det\!\Big(I+\tfrac{A_\eps}{2}\Big)
   -\tfrac14\log\det(I+A_\eps)
   = \frac{z^2}{16}\tr(K^2)+O(z^3).
\label{eq:s_Bhatt}
\end{align}
For nearby regular distributions the optimizing Chernoff parameter tends to
$s=\tfrac12$, so Eq.~\eqref{eq:s_Bhatt} is the leading Chernoff coefficient.

\paragraph*{Equality and boundary cases.}
With $z(\eps)=2c\,\eps+d\,\eps^2$, $c=x^{\!\top}G\delta$,
$d=\delta^{\!\top}G\delta>0$:
(i) fast class, $c\neq0$: $D=c^2\|K\|_F^2\eps^2+o(\eps^2)$, $m=1$;
(ii) curvature class, $c=0$, $d>0$: $D=\tfrac14 d^2\|K\|_F^2\eps^4+o(\eps^4)$,
$m=2$;
(iii) true local blindness only if $d=0$ (a nullspace of $G$ at coarse grain) or
the covariance signature is entirely nuisance;
(iv) global finite-change cancellation for signed changes at
$\eps_\ast=-2c/d$, so the theorem is local; on the monotone cone
($x\ge0$, $\delta\ge0$, $G$ entrywise nonnegative) $c,d\ge0$ and every $\eps>0$
gives $\Delta Q>0$;
(v) amplitude gauge: if $\Sigma=R+a\,Q(x)H$ then $\partial_a\Sigma=QH$ and
$\partial_Q\Sigma=aH$ are collinear, so zero-lag covariance carries zero
efficient information for separating $Q$ from $a$. Under nuisance profiling with
$\langle A,B\rangle_0=\tfrac12\tr(\Sigma_0^{-1}A\Sigma_0^{-1}B)$ and
$H_\perp=(I-\Pi_\eta)H$, Eqs.~\eqref{eq:s_KL}--\eqref{eq:s_Bhatt} hold with
$\|K_\perp\|_F$, $K_\perp=\Sigma_0^{-1/2}H_\perp\Sigma_0^{-1/2}$; if $H_\perp=0$
the change is unidentifiable from that ledger.

% =====================================================================
\section{JET\_TEST design and the seventeen frozen checks}
% =====================================================================
The jet test uses the exact scrambling generator (Sec.~S3) on a $32\times32$
grid ($N=1024$), code band $P_B=3$, grain band $K=13$, $M=36$ codes, and $10^4$
photons per bucket, with $\|K\|_F^2=3.46\times10^{-4}$. Three scene directions
are constructed: a generic beyond-band direction $\delta_g$ with
$c=x^{\!\top}G\delta_g\neq0$; an exactly $G$-orthogonal direction $\delta_o$ with
$x^{\!\top}G\delta_o=0$; and a small-eigenvalue direction $\delta_n$. A mixed
direction $\delta_{\mathrm{mix}}$ with a small nonzero $c$ probes the crossover.

Table~\ref{tab:jet_exp} lists the raw contact orders and coefficient ratios.
The exact-KL log--log slopes are $2.038$ ($\delta_g$) and $4.000$
($\delta_o,\delta_n$), matching the predicted integer orders; the measured
leading coefficients agree with Eqs.~\eqref{eq:s_KL}--\eqref{eq:s_Bhatt} to
$1.07\%$ ($\delta_g$) and $0.00\%$ ($\delta_o$). The Monte Carlo single-look
$d'\!\propto\!\eps^{m}$ exponents are $0.95$ and $2.05$; the CUSUM
($\mathrm{ARL}_0=500$, thresholds set by the ARL$_0$ approximation
of~\cite{s_Siegmund}) delay slopes are $-2.16$ and $-3.92$. These two CUSUM slopes
are two-point confirmations of the densely sampled ($12$-point, bank~A) exact-KL
contact orders, illustrative rather than independent fits. The mixed direction
crosses over at $\eps_{\mathrm{cross}}^{\mathrm{pred}}=9.995\times10^{-3}$ versus
empirical $9.997\times10^{-3}$ (ratio $1.0003$).

\begin{table}[h]
\centering
\caption{Raw jet exponents (committed \texttt{JET\_TEST}, \texttt{1bf29f1}).
$c=x^{\!\top}G\delta$, $d=\delta^{\!\top}G\delta$; KL slope is the log--log
regression of the exact Gaussian KL over an amplitude decade; coef.\ ratio is
measured/predicted leading coefficient.}
\label{tab:jet_exp}
\begin{ruledtabular}
\begin{tabular}{lcccccc}
Direction & $c$ & $d$ & $m_{\mathrm{pred}}$ & KL slope & Bhatt.\ slope & coef.\ ratio\\
\colrule
$\delta_g$ (generic)     & $29.78$              & $164.26$ & $1$ & $2.0381$ & $2.0374$ & $1.0107$\\
$\delta_o$ (orthogonal)  & $2.0\times10^{-15}$  & $137.43$ & $2$ & $3.9999$ & $3.9999$ & $1.0000$\\
$\delta_n$ (small eig.)  & $-3.1\times10^{-6}$  & $44.19$  & $2$ & $4.0000$ & $4.0000$ & $0.9999$\\
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}[h]
\centering
\caption{Monte Carlo and sequential-detection slopes, and the nuisance quotient
(committed \texttt{JET\_TEST}). $I_\theta$ is the per-bank efficient information
for $\log$ fluctuation scale; ``naive'' omits nuisance profiling.}
\label{tab:jet_mc}
\begin{ruledtabular}
\begin{tabular}{lcc}
Quantity & $\delta_g$ / value & $\delta_o$ / value\\
\colrule
MC $d'$ exponent $m$                   & $0.955$  & $2.046$\\
CUSUM delay slope                       & $-2.158$ & $-3.916$\\
\colrule
Amplitude gauge, single zero lag: $I_\theta^{\mathrm{naive}}$ & \multicolumn{2}{c}{$0.614$}\\
Amplitude gauge, single zero lag: $I_\theta^{\mathrm{eff}}$   & \multicolumn{2}{c}{$0.000$}\\
Amplitude gauge, proportional lags: $I_\theta^{\mathrm{eff}}$ & \multicolumn{2}{c}{$0.000$}\\
Second grain kernel: fraction recovered                       & \multicolumn{2}{c}{$0.018$}\\
Amplitude anchor: fraction recovered                          & \multicolumn{2}{c}{$0.200$}\\
\end{tabular}
\end{ruledtabular}
\end{table}

The signed iso-$Q$ cancellation crosses at $\eps_\ast=0.363$ with
$\mathrm{AUC}=0.481$ (chance), while the two sides remain visible
($\mathrm{AUC}=0.026$ and $1.000$), confirming locality. The monotone cone gives
$\Delta Q>0$ for all seven tested amplitudes ($\Delta Q$ from $1.59$ at
$\eps=0.005$ to $156.0$ at $\eps=0.4$), with the kernel entrywise nonnegative. A
scan of $400$ in-aperture directions gives $d_{\min}=\delta^{\!\top}G\delta=0.254$
(median $0.265$), so the blind fraction is exactly $0$. All seventeen frozen
checks pass and none of the four kill conditions fire (Table~\ref{tab:checks};
verdict \texttt{MOONSHOT\_SURVIVES}).

\begin{table}[h]
\centering
\caption{All seventeen predeclared JET\_TEST checks (committed
\texttt{JET\_TEST}, \texttt{1bf29f1}); every entry is \texttt{true}, and each of
the four kill conditions is \texttt{false}.}
\label{tab:checks}
\begin{ruledtabular}
\begin{tabular}{ll}
Check & Status\\
\colrule
1. KL contact order generic $=2$ & pass\\
2. KL contact order orthogonal $=4$ & pass\\
3. orders integer & pass\\
4. generic coefficient within $10\%$ & pass\\
5. orthogonal coefficient within $10\%$ & pass\\
6. crossover within $25\%$ & pass\\
7. delay slope generic near $-2$ & pass\\
8. delay slope orthogonal near $-4$ & pass\\
9. MC generic $m$ near $1$ & pass\\
10. MC orthogonal $m$ near $2$ & pass\\
11. amplitude gauge collapse to zero & pass\\
12. collapse persists across lags & pass\\
13. information returns with anchor & pass\\
14. AUC returns to $\tfrac12$ at $\eps_\ast$ & pass\\
15. locally visible either side of $\eps_\ast$ & pass\\
16. cone $\Delta Q>0$ for all tested & pass\\
17. no broad in-aperture blind set & pass\\
\colrule
Kills (non-integer order; $\eps^{-4}$ class vanished; & all\\
info survives collinear amplitude; broad blind set) & \texttt{false}\\
\end{tabular}
\end{ruledtabular}
\end{table}

% =====================================================================
\section{Full-scramble Gaussian derivation, generator, rank-one result, and duel}
% =====================================================================
A band-limited modulator imprints a real, nonnegative code $p_i$ (Fourier
support $B_p$) on the illumination; a dynamic strongly scattering medium with
state $T_t$ produces the speckle field $E_{i,t}(r)=\sum_a T_t(r,a)A_i(a)$, and a
single-pixel bucket collects $b_{i,t}=\sum_r |E_{i,t}(r)|^2 x(r)+\text{shot}$.
Fully developed speckle means $T_t$ has zero-mean circular-complex-Gaussian
entries, so $E_{i,t}$ is a zero-mean circular-complex-Gaussian field with
mutual coherence $J_{ij}(r,r')=\langle E_{i,t}(r)E_{j,t}(r')^{\ast}\rangle$.
With medium statistics
$\langle T_t(r,a)T_t(r',b)^{\ast}\rangle=C(r,r')\,\Gamma(a,b)$ and full
scrambling $\Gamma(a,b)=\tau(a)\delta_{ab}$, the coherence factorizes,
\begin{equation}
J_{ij}(r,r')=C(r-r')\,O_{ij},\qquad
O_{ij}=I_0\sum_a\tau(a)p_i(a)p_j(a).
\label{eq:s_factor}
\end{equation}
The joint field is exactly generated by $E_t=B(Z_t O^{1/2})$ with $Z_t$ i.i.d.\
unit circular-Gaussian, $O^{1/2}$ the code-covariance root, and $BB^{\dagger}=C$;
this Kronecker generator drives the simulation with no approximation.

\paragraph*{Mean wall.}
The mean intensity is $\mu_i(r)=J_{ii}(r,r)=C(0)O_{ii}$, independent of $r$, so
$\mathbb{E}[b_i]=C(0)O_{ii}\,\hat{x}(0)$: the first-moment channel measures only
the scene DC term, with spatial band $B_{\mathrm{mean}}=\{0\}$. Every $h$ with
$\hat{h}(0)=0$ is annihilated. Numerically the mean envelope coefficient of
variation is $0.0156$ (Monte Carlo floor $0.0158$), and the mean response to a
beyond-band, DC-free change has relative magnitude $6.56\times10^{-19}$.

\paragraph*{Covariance and rank collapse.}
By the Siegert relation $\mathrm{Cov}_t[S_{i,t}(r),S_{j,t}(r')]=|J_{ij}(r,r')|^2$,
so with Eq.~\eqref{eq:s_factor} the same-epoch bucket covariance collapses to
\begin{equation}
\mathrm{Cov}_t[b_{i,t},b_{j,t}]=O_{ij}^2\,Q(x),\qquad
Q(x)=\sum_{r,r'}x(r)x(r')|C(r-r')|^2=x^{\!\top}Gx .
\label{eq:s_Q}
\end{equation}
In Fourier, $Q(x)=\sum_k\hat{G}(k)|\hat{x}(k)|^2$ with $\hat{G}=\widehat{|C|^2}$
supported on $|k|\le2k_{\mathrm{grain}}$. The measured aperture is full
($\hat{G}$ nonzero on all $1024/1024$ bins, $C_0=0.517$), yet the scene enters
only through the scalar $Q$, so the covariance Fisher information is rank one,
$I^{\mathrm{cov}}_{xx}=4\kappa\,(Gx)(Gx)^{\!\top}$. Empirically
$\hat{Q}$ from $\mathrm{Var}[b_i]/O_{ii}^2$ is $190.9$ against the theoretical
$Q(x)=187.4$ (ratio $1.019$), and $99.99\%$ of the covariance matrix energy lies
in the single direction $O\!\circ\!O$. The change functional obeys
$\Delta Q=2x^{\!\top}G\delta+\delta^{\!\top}G\delta$; the predicted
$\Delta Q=0.34803$ matches the measured $0.34803$ to relative error
$2\times10^{-15}$, split into cross term $0.0031$ and quadratic term $0.3449>0$
for the orthogonal direction.

\paragraph*{Detection duel.}
Table~\ref{tab:duel} reports the H0-vs-H1 duel (efficient covariance score) at
the complete-scramble endpoint. The mean detector is at chance for both a
coherent and an orthogonal beyond-band $5\%$ change ($\mathrm{AUC}=0.502$ and
$0.505$), while the covariance detector reaches $d'=4.10$, $\mathrm{AUC}=0.997$
for the generic $5\%$ change at $8192$ banks. The worst-case orthogonal
direction obeys the predicted $d'\!\sim\!\eps^2\sqrt{T}$ law and is never zero;
its slower rate ($a=0.0050$ per $\sqrt{T}$ vs $0.0459$ for the coherent change)
is the curvature-class $\eps^{-4}$ price, not a blind direction.

\begin{table}[h]
\centering
\caption{Complete-scramble detection (committed \texttt{SCRAMBLE\_EXT},
\texttt{ed7a1e0}). $d'$ and AUC at listed bank budgets $T_{\mathrm{eff}}$; the
mean detector uses $512$ banks. ``coherent'' is a generic direction
($x^{\!\top}G\delta\neq0$); ``orthogonal'' is $G$-orthogonal.}
\label{tab:duel}
\begin{ruledtabular}
\begin{tabular}{lccc}
Channel / change & $T_{\mathrm{eff}}$ & $d'$ & AUC\\
\colrule
Mean, coherent $5\%$        & $512$   & $0.030$ & $0.502$\\
Mean, orthogonal $5\%$      & $512$   & $0.015$ & $0.505$\\
Covariance, coherent $5\%$  & $512$   & $0.99$  & $0.762$\\
Covariance, coherent $5\%$  & $2048$  & $2.22$  & $0.943$\\
Covariance, coherent $5\%$  & $8192$  & $4.10$  & $0.997$\\
Covariance, coherent $2\%$  & $8192$  & $1.60$  & $0.887$\\
Covariance, orthogonal $5\%$& $8192$  & $0.36$  & $0.601$\\
Covariance, orthogonal $5\%$& $65536$ & $1.23$  & $0.809$\\
\end{tabular}
\end{ruledtabular}
\end{table}

% =====================================================================
\section{Sealed thin-screen protocol, bars D0--D6, comparator, and audits}
% =====================================================================
The sealed sentinel uses a true zero-dimensional bucket record on a $64\times64$
scene ($N=4096$), modulator band $k_p=5$, $M=128$ signed effective codes realized
by $256$ complementary nonnegative exposures per bank at a $20\,\mathrm{kHz}$
pattern rate ($12.8\,\mathrm{ms}$ per bank; cap $T_{\mathrm{eff}}=4096$ banks
$=52.4\,\mathrm{s}$), $10^4$ detected photoelectrons per physical bucket, and a
medium quasi-static within a bank and independent between banks. Thresholds were
committed before confirmatory generation; the run used $12$ confirmatory banks and
$2.76$ of a $6.0$ GPU-hour ceiling. Table~\ref{tab:bars} summarizes the seven
bars.

\begin{table}[h]
\centering
\caption{Sealed detector bars D0--D6 (committed \texttt{SEALED\_DET/CONFIRMATORY},
\texttt{b37c841}; analysis freeze \texttt{5910277}). ``passed'' is the frozen
bar verdict; D3 and D5 did not pass their strong forms but did not trigger a
kill, defining the honest boundary (Sec.~S4).}
\label{tab:bars}
\begin{ruledtabular}
\begin{tabular}{llc}
Bar & Key measured endpoint & Verdict\\
\colrule
D0 mechanism/engine & mean deriv.\ $5.7\times10^{-16}$; two-engine $1.7\%$; shot ledger $1.0\%$ & pass\\
D1 calibration      & $n=108$ cells, median $d'_{\mathrm{emp}}/d'_{\mathrm{an}}=0.998$, all in $[0.91,1.10]$ & pass\\
D2 capability       & $2\%$ in $77/81$ cells, best $453$ banks, MC power LCB $0.990$ & pass\\
D3 specificity      & TPR $0.988$, bal.\ acc.\ $0.916$; medium FA $0.096/0.084>0.05$ & boundary\\
D4 fresh comparator & fixed vs fresh latency $459$ vs $1013$ banks (retain fixed) & pass\\
D5 mismatch         & AUC $1.000$; $\le10\%$ rotation passes; $20\%$/slope$-1$ fail & boundary\\
D6 online feasibility & $0.0203\,\mathrm{ms}$ ($0.16\%$ of bank), $0.26\,\mathrm{MB}$ & pass\\
\end{tabular}
\end{ruledtabular}
\end{table}

\paragraph*{D2 capability.}
The $2\%$ beyond-band change is analytically detectable within the $4096$-bank
cap in $77/81$ predeclared cells; the best cell (unit static factor, $k^{-2}$
spectrum, $k_w/k_p=1$, $1.25k_p$ claim shell) requires $453$ banks and the pooled
Monte Carlo power lower bound is $0.990$ ($n=13500$). The $5\%$ change clears all
$81$ energy-spread cells and $75/81$ worst-mode cells; the $1\%$ best cell clears
$d'\ge5$ by $1811$ banks; the $0.5\%$ edge audit reaches $d'_{\max}=3.76$.

\paragraph*{D3 specificity (strong claim killed, power intact).}
At the threshold calibrated to $1\%$ H0 false alarm ($t=0.051$), the target
true-positive rate is $0.988$, in-band false alarms are $0.020$, and four-class
balanced accuracy is $0.916$; the beyond score stays centered on non-targets
($|d'|\le0.019$) and the attribution-simplex maximum off-diagonal canonical
correlation is $0.039$. However, medium-amplitude and medium-timescale events
exceed the frozen $0.05$ false-alarm bar at $0.096$ and $0.084$, and the weakest
class-specific separation is $1.79$ rather than $5$ (the intended per-class
separations are $[1.79,\,43.06,\,4.78]$). The result is a power-certified
beyond-band alarm with measured attribution leakage, not a fully specific
sentinel; no ``specific'', ``zero-false-alarm'', or ``medium-immune'' wording is
used.

\paragraph*{D4 fixed-versus-fresh.}
On identical photons, exposures, duration, anomaly bank, and law knowledge, the
repeated (fixed) code bank retains a latency advantage: best cell $459$ (fixed)
versus $1013$ (fresh) banks, mid cell $1271$ versus $1488$, floor cell $1598$
versus $3334$; the frozen branch retains the fixed-code concentration.

\paragraph*{D5 mismatch (robustness frozen to $\le10\%$ rotation).}
AUC is $1.000$ on every tested axis and latency inflation is bounded, but
false-alarm calibration fails outside the primary domain: at aperture-preserving
basis rotation $10\%$ the non-target false alarm is $0.032$ (latency inflation
$19\%$, pass), whereas at $20\%$ rotation it is $0.052$ and at spectral-slope
mismatch $-1$ it is $0.076$ (fail). Robustness is therefore frozen to the
$\le10\%$ rotation regime; the kill-tree verdict is ``narrow the physical domain
or kill robustness wording'', and the broader wording is withdrawn.

\paragraph*{Integrity audits (verbatim).}
\emph{Record generator.} After protocol freeze and before unblinding, the record
generator was refactored solely to stream Monte Carlo records in GPU-memory
chunks; an audited diff found no changes to hypotheses, thresholds, bank counts,
scenes, estimators, or endpoints, although altered random-number consumption
produced a different, still-blinded realization set. All reported decisions apply
the frozen analysis unchanged to that disclosed chunked stream.
\emph{Shot model.} A mandated independent-engine check exposed a signed-code
shot-noise error that had inflated covariance Fisher information by approximately
$1.9\times$; replacing the signed difference $Px$ with the physical
complementary-exposure throughput $|P|x$ reduced the frozen $P1$ witness coverage
from $0.050$ to $0.033$ and eliminated the apparent natural-scene living pocket,
so all values reported here come from the corrected artifacts and every prior
kill only strengthened.

% =====================================================================
\section{Thin-screen covariance aperture and minimal prior-art fence}
% =====================================================================
\paragraph*{Aperture interpolation.}
The thin multiplicative screen is the weakest complex medium: a single random
phase layer $w_t$. Its bucket covariance is
$C(x)=\Phi^2 P\,\mathrm{diag}(x)K_w\,\mathrm{diag}(x)P^{\!\top}$, whose informative
support is the convolution aperture $B_w\oplus B_p$ and whose Fisher structure is
rich---many recoverable scene modes. As the medium approaches complete
scrambling, the input coupling $\Gamma$ loses angular memory
(rank $r_{\mathrm{ME}}\to1$) and the covariance factorizes as in
Eq.~\eqref{eq:s_factor}, collapsing all $M(M+1)/2$ entries to the single scalar
$Q(x)$. For a residual memory effect of rank $r_{\mathrm{ME}}$ the covariance
becomes a rank-$O(r_{\mathrm{ME}}^2)$ combination of quadratic scene functionals,
so the recoverable imaging aperture interpolates monotonically from the rich
thin-screen aperture to the rank-one scalar. \emph{Beyond-band imaging survives
exactly to the extent the medium retains memory-effect modes; beyond-band
detection survives complete scrambling}, because $\delta^{\!\top}G\delta>0$ for
every nonzero $\delta$. This is the precise, physically correct boundary between
the two disorder endpoints of the Letter.

\paragraph*{Minimal prior-art fence.}
The result is distinct from the head-on prior art. Memory-effect imaging through
opaque scattering layers~\cite{s_Bertolotti,s_Katz,s_Freund} \emph{reconstructs}
a hidden object while residual angular correlations survive; we operate at the
endpoint where reconstruction rank is one and only the observability order
survives. Blind structured-illumination and speckle-superresolution
imaging~\cite{s_Mudry,s_Idier} and photoacoustic speckle-fluctuation
imaging~\cite{s_Chaigne} likewise \emph{reconstruct} by exploiting residual
correlations; our contribution is the opposite regime. Quantum-inspired
superresolution~\cite{s_Tsang} moves Fisher information between optical
\emph{measurements} of the same scene, and quantum change
detection~\cite{s_GraceGuha} optimizes quantum-limited discrimination of a
\emph{known} object change; the Rank--Jet Separation instead moves contact order
between \emph{statistical layers} of one scalar classical record and classifies a
\emph{nuisance-profiled} contact order, with no change of hardware.
Speckle-decorrelation and coda-wave change detection~\cite{s_Snieder} and SAR
coherent change detection~\cite{s_SAR_CCD} sense inter-pass decorrelation of the
\emph{medium}; here an exact first-moment invariance wall makes the medium a
transducer for \emph{scene} change while a profiled quotient rejects medium-law
events. Mesoscopic universal conductance fluctuations~\cite{s_LeeStone} are the
disorder-statistics ancestor of the covariance channel but carry no
detection-order classification. No claim of prior-art equivalence is made, and the
novelty is the nuisance-profiled statistical jet order as a physical observability
class for disordered sensing.

\begin{thebibliography}{99}
\bibitem{s_Mudry} E. Mudry \textit{et al.}, Nat. Photonics \textbf{6}, 312 (2012).
\bibitem{s_Idier} J. Idier \textit{et al.}, IEEE Trans. Comput. Imaging \textbf{4}, 87 (2018).
\bibitem{s_Chaigne} T. Chaigne \textit{et al.}, Optica \textbf{3}, 54 (2016).
\bibitem{s_Tsang} M. Tsang, R. Nair, and X.-M. Lu, Phys. Rev. X \textbf{6}, 031033 (2016).
\bibitem{s_Snieder} R. Snieder, A. Gr\^et, H. Douma, and J. Scales, Science \textbf{295}, 2253 (2002).
\bibitem{s_Bertolotti} J. Bertolotti, E.~G. van Putten, C. Blum, A. Lagendijk, W.~L. Vos, and A.~P. Mosk, Nature \textbf{491}, 232 (2012).
\bibitem{s_Katz} O. Katz, P. Heidmann, M. Fink, and S. Gigan, Nat. Photonics \textbf{8}, 784 (2014).
\bibitem{s_Freund} I. Freund, M. Rosenbluh, and S. Feng, Phys. Rev. Lett. \textbf{61}, 2328 (1988).
\bibitem{s_GraceGuha} M.~R. Grace and S. Guha, Phys. Rev. Lett. \textbf{129}, 180502 (2022).
\bibitem{s_SAR_CCD} M. Preiss and N.~J.~S. Stacy, \textit{Coherent Change Detection: Theoretical Description and Experimental Results}, DSTO-TR-1851 (2006).
\bibitem{s_LeeStone} P.~A. Lee and A.~D. Stone, Phys. Rev. Lett. \textbf{55}, 1622 (1985).
\bibitem{s_Siegmund} D. Siegmund, \textit{Sequential Analysis: Tests and Confidence Intervals} (Springer, New York, 1985).
\end{thebibliography}

\end{document}
